---
title: "Parkinson's cross-sectional study analysis"
author: "Jade Pickering"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    number-sections: true
editor: visual
execute:
  echo: true
  warning: false
  message: false
---

## Overview

This doc runs the analysis scripts and reports the results for the data from people with Parkinson’s (PwP) and health age-matched controls (HCs).\
Each section sources a dedicated R script from the `scripts/` folder.

## Setup

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
# Load packages
library(tidyverse)
library(janitor)
library(here)

# Define paths
raw_data_dir <- here("raw_data")
tidied_data_dir <- here("tidied_data")
scripts_dir <- here("scripts")
plots_dir <- here("plots")
```

## Dummy data

For the purposes of writing the script I want to work with dummy data to avoid accessing the real data unnecessarily, which is stored on a network drive. Added bonus of not taking a very long time to run each time.

To do:

-   ~~Demographics and questionnaire data~~

-   Go/No-Go

-   Stop Signal task

-   Eriksen Flanker

-   ~~Stroop~~

-   ~~Trail Making~~

-   Balloon Analogue Risk Task

-   Iowa Gambling Task

-   Cambridge Gambling Task

-   Kirby Monetary Choice Questionnaire

-   ~~Barratt Impulsiveness Scale~~

-   ~~Behavioural Approach/Inhibition Systems~~

-   ~~UPPS-P~~

```{r}
# Run the dummy data generation
source(generate_dummy_data.R)

```

## Demographics

## Questionnaire

## Go/No-Go

```{r}
# Run the GNG analysis code
source(scripts/go-no-go.R)
```
